STA610 Case Study 1 Team 4 Report

### 2021-03-22 STA_610_Case_Study_1_Report_Team_4.Rmd
updated the intro

>>>>

Our drug of interest in this study is oxymorphone. Oxymorphone is used to relieve moderate to severe pain in people whose pain is not controlled with other medications, and may be habit-forming with prolonged use. Our aim is to investigate factors related to the price per mg of oxymorphone, accounting for potential clustering by location and exploring heterogeneity in pricing by location.
